---
title: "CherAnalysis"
output:
  html_document:
    code_folding: hide
    theme: yeti
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
  word_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(broom)
library(broom.mixed)
library(reshape2)

## Stats
library(lme4)      # Mixed models
library(lmerTest)
library(modeest)   # Mode estimation
library(vcd)       # Fit of count data
library(sjPlot)
library(pscl)
library(readr)

## Graphics
library(ggplot2)
library(ggthemes)
library(ggExtra)
library(ggsci)
library(scales)
library(viridis)

## tables
library(kableExtra)
library(xtable)
```


# Load

Load all subjects

```{r}
bdata <- read_csv("../gambling_clean_data.csv", show_col_types = F)
```




Load the model assignments

```{r}
assignments <- read_csv("../LL_model2.csv", show_col_types = FALSE)
```

Merge the two, to make sure we have the same data

```{r}
full <- full_join(bdata, assignments, by="HCPID")
#full <- full %>% filter(!is.na(BlockType), !is.na(TrialType))
```


# Group Differences in Response Switch

```{r}
adata_feedback <- full %>%
  group_by(HCPID, TrialType) %>%
  filter(!is.na(ResponseSwitch)) %>%
  summarise(ResponseSwitch = mean(ResponseSwitch),
            RT = mean(RT),
            Model=mlv(best.model),
            deltaLL = mean(diff.LL)) %>%
  #rename(Block = BlockTypeCoded) %>%
  #mutate(Block = recode(Block, MostlyReward = "Mostly Wins", MostlyPunishment = "Mostly Losses")) %>%
  mutate(TrialType = recode(TrialType, Reward = "Win", Punishment = "Loss", Neutral = "Neutral"))



```

And now, let's visualize
```{r, fig.width=5, fig.height=5}
ggplot(adata_feedback, aes(x=TrialType, y=ResponseSwitch, col=Model)) +
  #facet_wrap(~Block) +
  stat_summary(geom="point", fun.data="mean_se", size=3) +
  stat_summary(geom="errorbar", fun.data = "mean_se", width=0.1) +
  stat_summary(geom="line", aes(group=Model), fun.data="mean_se") +
  coord_cartesian(ylim=c(0, .75)) +
  ylab("Probability of Changing Response") +
  xlab("Trial Type") +
  ggtitle("Group Differences in Responses") +
  scale_color_d3() +
  theme_minimal() +
  theme(legend.position = "bottom")

ggsave("responseswitch.png", dpi=72)
```

The analysis reveal a main effect of Model (Group):

```{r}
mod_feedback <- glmer(ResponseSwitch ~ best.model *  TrialType + (1|HCPID),  family="binomial", weights=abs(diff.LL), data=filter(full, !is.na(ResponseSwitch)))

mod_feedback %>%
  tidy() %>%
  kable() %>%
  kable_styling(bootstrap_options=c("striped", "hover"))

tab_model(mod_feedback)
```


# Group Differences in Persistance

Now, let's look at the data by block:

```{r, fig.width=5, fig.height=5}
adata_block <- full %>%
  group_by(HCPID, BlockTypeCoded) %>%
  summarise(Persistance = mean(ConsecSameResp),
            MaxPersistance = max(ConsecSameResp),
            RT = mean(RT),
            Model=mlv(best.model),
            deltaLL = mean(diff.LL)) %>%
  rename(Block = BlockTypeCoded) %>%
  mutate(Block = recode(Block, MostlyReward = "Mostly Wins", MostlyPunishment = "Mostly Losses")) 



ggplot(adata_block, aes(x=Block, y=Persistance, col=Model)) +
  stat_summary(geom="point", fun.data="mean_se", size=3) +
  stat_summary(geom="errorbar", fun.data = "mean_se", width=0.1) +
  stat_summary(geom="line", aes(group=Model), fun.data="mean_se") +
  xlab("Block Type") +
  ylab("Max Consecutive Identical Responses") +
  ggtitle("Persistence by Model and Block Type") +
  scale_color_d3() +
  theme_minimal()

ggsave("persistance.png", dpi=72)
```

To analyze this, we will use generalized linear model with a Poisson distribution. The choice of a Poisson distribution is given by the fact that the distribution of longest consecutive streaks (persistance) should obey a Poisson. Just in case, here is the actual distribution.

```{r}
ggplot(adata_block, aes(x=MaxPersistance, fill=Model)) +
  geom_histogram(col="white", alpha=0.5, position = "identity", bins=15) +
  scale_fill_d3() +
  theme_minimal()

ggplot(adata_block, aes(x=MaxPersistance, fill=Model)) +
  geom_density(col="white", alpha=0.5, position = "identity", bw=4) +
  scale_fill_d3() +
  theme_minimal()
```



We first fit a Poisson model

```{r}

mod1 <- glm(MaxPersistance ~ Model * Block,  family="poisson", weights=abs(adata_block$deltaLL), data=adata_block)

mod1 %>%
  tidy() %>%
  kable() %>%
  kable_styling(bootstrap_options=c("striped", "hover"))

tab_model(mod1)
```

It is possible to conceptualize the Max Persistance count as a Negative binomial

```{r}
mod2 <- MASS::glm.nb(MaxPersistance ~ Model * Block,  weights=abs(adata_block$deltaLL), data=adata_block)

mod2 %>%
  tidy() %>%
  kable() %>%
  kable_styling(bootstrap_options=c("striped", "hover"))

tab_model(mod2)

```

Neither one first the data _too_ well, TBH, but they do fit better than a normal distribution.

```{r}
gf <- goodfit(adata_block$MaxPersistance, type= "nbinomial",method= "ML")
summary(gf)
plot(gf,main="Count data vs Negative Binomial distribution")

gf <- goodfit(adata_block$MaxPersistance, type= "poisson",method= "ML")
summary(gf)
plot(gf,main="Count data vs Poisson distribution")
```


# Group Differences in Response Times.

Then, we look at differences in RTs

```{r, fig.width=5, fig.height=5}
ggplot(adata_block, aes(x=Block, y=RT, col=Model, group=Model)) +
  stat_summary(geom="point", fun.data="mean_se", size=3) +
  stat_summary(geom="errorbar", fun.data = "mean_se", width=0.1) +
  stat_summary(geom="line", aes(group=Model), fun.data="mean_se") +
  ylab("Response Times (ms)") +
  ggtitle("Group Differences in Response Times") +
  scale_color_d3() +
  theme_minimal() +
  theme(legend.position = "bottom")

ggsave("responsetimes.png", dpi=72)
```


```{r}
mod3 <- glmer(log(RT) ~ Model * Block + (1|HCPID), family="Gamma", weights = abs(deltaLL), adata_block)
tab_model(mod3)
```